---
title: "ggr intro"
author: "JF Rami"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r}
library(ggr)
library(knitr)
```


Let's read two example files provided with the package

```{r}
mymap<-read.table(system.file("extdata","Nguepjop.et.al.2016.map.txt",package="ggr"))
myg<-read.table(system.file("extdata","Nguepjop.et.al.2016.txt",package="ggr"))
```

The files look like that:

```{r, echo=FALSE}
kable(head(mymap))
kable(head(myg))
```

The map needs to be converted to the R/qtl format

```{r}
mymap<-as.map(mymap)
mymap
```

Let's get the genotype codes that are used in the genotype table myg :

```{r}
codes<-unique(c(as.matrix(myg[,-1])))
codes
```

We will need a vector of named colors, using codes as names, to plot the genotypes blocs
```{r}
mycolors<-c("green","yellow","red","white")
names(mycolors)<-codes
mycolors
```


Let's use the `gg` function with myg, mymap and mycolors. There is a couple of parameters to explore, especially parameters of the `maplot` function that is used to plot the map.

```{r, fig.width=10, fig.height=6}
gg(x = myg,map = mymap,col =mycolors,lmarg = 0.06 ,inter=0.1,first = 0.05,position=F,decalcoef = 0.005, sw=-1)

```


